Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
wip

	Next,
	we bound  costs incurred by \OPT for requests that trigger collocation of $\{u,v\}$ at $t \in T$.
	If $t$ is the first time that \RM collocates $\{u,v\}$,
	 then  \OPT pays
	$\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	or $\alpha$ for collocating the pair and
	serving (some of) the requests with  cost zero.
	Therefore in this case,
	$\OPT(\sigma_{\{u,v\}}(0,t]) \geq  \min{\{ \lambda,\alpha \}}$.
	%
	Otherwise,
	it is not the first collocation and
	consider times $t'$ and $t''$ as define previously,
	 and let 
	$R_t := \sigma_{\{u,w\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t] $.
	We define $R_{t'}$ for the collocation at $t'$  analogously.
	Then,
	$\OPT(R_t) =\OPT (\sigma_{\{u,w\}}) 
	+ \OPT(\sigma_{\{u,v\}}) $.
	If \OPT has both pairs separated during their respective intervals,
	then obviously it pays $2\lambda$ during those intervals.
	Note that \OPT cannot have both pairs collocated at the same time.
%	However, it can have one of the pairs already collocated prior to its respective interval.
	Let us assume \OPT has one of the pairs,
	e.g.~$\{u,v\}$,
	 collocated already prior its respective interval, $(t',t]$,
	 and keeps it so during the interval.
	 Then it pays zero while serving $\sigma_{\{u,v\}}$.
	Hence,
	it must pay $\alpha$ for collocating the other pair, in this case $\{u,w\}$,
	or (resp., and) it pays (resp., up to) $\lambda$ for serving (resp., some of) requests in $\sigma_{\{u,w\}}$. 
	Therefore in any case,
	$\OPT(R_t) \geq  \min{\{ \lambda,\alpha \}} = \alpha$.

>>>>

	Next,
	we bound  costs incurred by \OPT for requests that trigger collocation of $\{u,v\}$ at $t \in T$.
	If $t$ is the first time that \RM collocates $\{u,v\}$,
	 then  \OPT pays
	$\lambda$ for serving requests in $\sigma_{\set{u,v}}[0,t]$ (remotely),
	or $\alpha$ for collocating the pair and
	serving (some of) the requests with  cost zero.
	Therefore in this case,
	$\OPT(\sigma_{\{u,v\}}(0,t]) \geq  \min{\{ \lambda,\alpha \}}$.
	%
	Otherwise,
	it is not the first collocation and
	consider times $t'$ and $t''$ as defined previously,
	 and let 
	$R_t := \sigma_{\{u,w\}}(t'',t'] \cup \sigma_{\{u,v\}}(t',t] $.
	We define $R_{t'}$ for the collocation at $t'$  analogously.
	Then,
	$\OPT(R_t) =\OPT (\sigma_{\{u,w\}}) 
	+ \OPT(\sigma_{\{u,v\}}) $.
	If \OPT has both pairs separated during their respective intervals,
	then obviously it pays $2\lambda$ during those intervals.
	Note that \OPT cannot have both pairs collocated at the same time.
%	However, it can have one of the pairs already collocated prior to its respective interval.
	Let us assume \OPT has one of the pairs,
	e.g.~$\{u,v\}$,
	 collocated already prior its respective interval, $(t',t]$,
	 and keeps it so during the interval.
	 Then it pays zero while serving $\sigma_{\{u,v\}}$.
	Hence,
	it must pay $\alpha$ for collocating the other pair, in this case $\{u,w\}$,
	or (resp., and) it pays (resp., up to) $\lambda$ for serving (resp., some of) requests in $\sigma_{\{u,w\}}$. 
	Therefore in any case,
	$\OPT(R_t) \geq  \min{\{ \lambda,\alpha \}} = \alpha$.
